EldersAIR initial home/adult data work

### 2020-02-21 home_adult_data_cleaning.Rmd
pm and medical visit cleaning

---
title: "EldersAIR initial home/adult data work"
author: "Ethan Walker"
date: "Started 10 Feb 2020, Updated 10 Feb 2020"
output: pdf_document
---

@@

# Load, format, and save home and adult overview/demographic data for NP
```{r}
# Load files 
## Box location: Update Box location once final data loaded
np_adult_initial <- read_csv("Input/NP/np_adults_20200210.csv") %>% 
  rename_all(tolower) %>% 
  mutate(adult_hwid = as.factor(adulthwid),
         home_id = as.factor(homeid),
         adult_id = as.factor(adultid),
         home_winter_id = as.factor(homewinterid)) %>% 
  select(adult_hwid, home_id, adult_id, home_winter_id)

## Box location: Update Box location once final data loaded
np_home_initial <- read_csv("Input/NP/np_home_20200210.csv") %>% 
  rename_all(tolower) %>% 
  mutate(home_id = as.factor(homeid),
         winter_id = as.factor(winterid),
         home_winter_id = as.factor(homewinterid),
         intervention_date = ymd(interventiondate),
         intervention_time = as.character(interventiontime),
         sampling_date_1 = ymd(samplingdate),
         sampling_time_1 = as.character(samplingtime),
         pickup_date_1 = ymd(pickupdate),
         pickup_time_1 = as.character(pickuptime),
         sampling_date_2 = ymd(sampling2date),
         sampling_time_2 = as.character(sampling2time),
         pickup_date_2 = ymd(pickup2date),
         pickup_time_2 = as.character(pickup2time),
         home_qaqc_comments = as.character(qaqchccomments)) %>% 
  select(home_id, winter_id, home_winter_id, intervention_date, intervention_time,
         sampling_date_1, sampling_time_1, pickup_date_1, pickup_time_1,
         sampling_date_2, sampling_time_2, pickup_date_2, pickup_time_2,
         home_qaqc_comments) 
```

# Load, format, and save home and adult overview/demographic data for NN
```{r}
# Load files 
## Box location: Update Box location once final data loaded
nn_adult_initial <- read_csv("Input/NN/nn_adults_20200210.csv") %>% 
  rename_all(tolower) %>% 
  mutate(adult_id = as.factor(adultid),
         home_id = as.factor(homeid),
         adult_id_char = as.factor(id),
         adult_hispanic = as.factor(hispanic),
         adult_race = as.factor(race),
         adult_gender = as.factor(gender)) %>% 
  select(adult_id, home_id, adult_id_char, adult_hispanic, 
         adult_race, adult_gender)

## Box location: Update Box location once final data loaded
nn_home_initial <- read_csv("Input/NN/nn_home_20200210.csv") %>% 
  rename_all(tolower) %>% 
  mutate(home_id = as.factor(homeid),
         winter_id = as.factor(winterid),
         home_winter_id = as.factor(homewinterid),
         intervention_date = ymd(interventiondate),
         intervention_time = as.character(interventiontime),
         sampling_date_1 = ymd(samplingdate),
         sampling_time_1 = as.character(samplingtime),
         pickup_date_1 = ymd(pickupdate),
         pickup_time_1 = as.character(pickuptime),
         sampling_date_2 = ymd(sampling2date),
         sampling_time_2 = as.character(sampling2time),
         pickup_date_2 = ymd(pickup2date),
         pickup_time_2 = as.character(pickup2time),
         home_qaqc_comments = as.character(qaqchccomments)) %>% 
  select(home_id, winter_id, home_winter_id, intervention_date, intervention_time,
         sampling_date_1, sampling_time_1, pickup_date_1, pickup_time_1,
         sampling_date_2, sampling_time_2, pickup_date_2, pickup_time_2,
         home_qaqc_comments) 
```

################ Past this point is from KidsAIR data cleaning
################ Use to finalize Elders code once all data is available

```{r}
## Box location: Update Box location once final data loaded
wmt_homewinter_initial <- read_xlsx("Input/WMT/wmt_homewinter_20191126.xlsx") %>% 
  rename_all(tolower) %>% 
  select(homewinterid, homeid, winterid, interventiondate, interventiontime) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         home_id = as.character(homeid),
         winter_id = as.character(winterid),
         intervention_date = interventiondate,
         intervention_time = interventiontime) %>% 
  select(home_winter_id, home_id, winter_id, intervention_date, intervention_time)
## Box location: Update Box location once final data loaded
wmt_parent_demographics_initial <-
  read_xlsx("Input/WMT/wmt_parent_demographics_20191126.xlsx") %>% 
  rename_all(tolower) %>% 
  select(homewinterid, gender, hispanic, race, income, education,
         totalres, underfive) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         gender_parent = as.factor(gender),
         hispanic_parent = as.factor(hispanic),
         race_parent = as.factor(race),
         income = as.factor(income),
         education = as.factor(education),
         total_residents = as.character(totalres),
         residents_under_five = as.character(underfive)) %>% 
  select(home_winter_id, gender_parent, hispanic_parent, race_parent,
         income, education, total_residents, residents_under_five) %>% 
  filter(!is.na(gender_parent))
# join all files from above
joined1 <- wmt_homewinter_initial %>% 
  left_join(wmt_parent_demographics_initial, by = "home_winter_id") %>% 
  left_join(wmt_home_initial, by = "home_id") %>% 
  left_join(wmt_child_initial, by = "home_id") %>% 
  mutate(area = "WMT")

# create dataset of id's and treatment assignment
wmt_home_ids_linked <- joined1 %>% 
  select(area, home_id, winter_id, home, home_winter_id, treatment) %>% 
  distinct(home_winter_id, .keep_all = TRUE) %>% 
  arrange(home_id, winter_id)

# create dataset of child demographic data
wmt_child_demographics <- joined1 %>% 
  #distinct(child_id_num, .keep_all = TRUE) %>% 
  arrange(home_id, child_id_num, winter_id) %>% 
  filter(winter_id == 1 | winter_id == 2) 
# Save as RDS and CSV
write_rds(wmt_home_ids_linked, "Output/wmt_ids_linked.rds")
write_rds(wmt_child_demographics, "Output/wmt_demographic_data.rds")
```

# Load, format, and save home and child overview/demographic data for NN
```{r}
# Load files
## Box location: All Files > NoonGroupData > KidsAIR > 
## 2019-November-Data > Navajo > child.xlsx
nn_child_initial <- read_xlsx("Input/NN/nn_child_20191216.xlsx") %>% 
  rename_all(tolower) %>% 
  select(childid, homeid, id, hispanic, race, agenov1, enrolled) %>% 
  mutate(child_id_num = as.character(childid),
         home_id = as.character(homeid),
         child_id_char = as.character(id),
         hispanic_child = as.factor(hispanic),
         race_child = as.factor(race),
         age_child_nov = as.character(agenov1)) %>% 
  select(child_id_num, home_id, child_id_char, hispanic_child,
         race_child, age_child_nov, enrolled) 
## Box location: All Files > NoonGroupData > KidsAIR > 
## 2019-November-Data > Navajo > home.xlsx
nn_home_initial <- read_xlsx("Input/NN/nn_home_20191216.xlsx") %>% 
  rename_all(tolower) %>% 
  select(homeid, home, txcondition) %>% 
  mutate(home_id = as.character(homeid),
         home = as.character(home),
         treatment = as.factor(txcondition)) %>% 
  select(home_id, home, treatment)
## Box location: All Files > NoonGroupData > KidsAIR > 
## 2019-November-Data > Navajo > homewinter.xlsx
nn_homewinter_initial <- read_xlsx("Input/NN/nn_homewinter_20191216.xlsx") %>% 
  rename_all(tolower) %>% 
  select(homewinterid, homeid, winterid, interventiondate, interventiontime) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         home_id = as.character(homeid),
         winter_id = as.character(winterid),
         intervention_date = interventiondate,
         intervention_time = interventiontime) %>% 
  select(home_winter_id, home_id, winter_id, intervention_date, intervention_time)
## Box location: All Files > NoonGroupData > KidsAIR > 
## 2019-November-Data > Navajo > Home Data > parentdemographics.xlsx
nn_parent_demographics_initial <-
  read_xlsx("Input/NN/nn_parent_demographics_20191216.xlsx") %>% 
  rename_all(tolower) %>% 
  select(homewinterid, gender, hispanic, race, income, education,
         totalres, underfive) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         gender_parent = as.factor(gender),
         hispanic_parent = as.factor(hispanic),
         race_parent = as.factor(race),
         income = as.factor(income),
         education = as.factor(education),
         total_residents = as.character(totalres),
         residents_under_five = as.character(underfive)) %>% 
  select(home_winter_id, gender_parent, hispanic_parent, race_parent,
         income, education, total_residents, residents_under_five) %>% 
  filter(!is.na(gender_parent))
# join all files from above
joined1 <- nn_homewinter_initial %>% 
  left_join(nn_parent_demographics_initial, by = "home_winter_id") %>% 
  left_join(nn_home_initial, by = "home_id") %>% 
  left_join(nn_child_initial, by = "home_id") %>% 
  mutate(area = "NN")

# create dataset of id's and treatment assignment
nn_home_ids_linked <- joined1 %>% 
  select(area, home_id, winter_id, home, home_winter_id, treatment) %>% 
  distinct(home_winter_id, .keep_all = TRUE) %>% 
  arrange(home_id, winter_id)

# create dataset of child demographic data
nn_child_demographics <- joined1 %>% 
  #distinct(child_id_num, .keep_all = TRUE) %>% 
  arrange(home_id, child_id_num, winter_id) %>% 
  filter(winter_id == 1 | winter_id == 2) 
# Save as RDS and CSV
write_rds(nn_home_ids_linked, "Output/nn_ids_linked.rds")
write_rds(nn_child_demographics, "Output/nn_demographic_data.rds")
```

# Load, format, and save home and child overview/demographic data for AK
```{r}
# Load files 
## Box location: All Files > NoonGroupData > KidsAIR > 
## 2019-November-Data > AK > child.xlsx
ak_child_initial <- read_xlsx("Input/AK/ak_child_20191216.xlsx") %>% 
  rename_all(tolower) %>% 
  select(childid, homeid, id, hispanic, race, agenov1, enrolled) %>% 
  mutate(child_id_num = as.character(childid),
         home_id = as.character(homeid),
         child_id_char = as.character(id),
         hispanic_child = as.factor(hispanic),
         race_child = as.factor(race),
         age_child_nov = as.character(agenov1)) %>% 
  select(child_id_num, home_id, child_id_char, hispanic_child,
         race_child, age_child_nov, enrolled) 
## Box location: All Files > NoonGroupData > KidsAIR > 
## 2019-November-Data > AK > home.xlsx
ak_home_initial <- read_xlsx("Input/AK/ak_home_20191216.xlsx") %>% 
  rename_all(tolower) %>% 
  select(homeid, home, txcondition) %>% 
  mutate(home_id = as.character(homeid),
         home = as.character(home),
         treatment = as.factor(txcondition)) %>% 
  select(home_id, home, treatment)
## Box location: All Files > NoonGroupData > KidsAIR > 
## 2019-November-Data > AK > homewinter.xlsx
ak_homewinter_initial <- read_xlsx("Input/AK/ak_homewinter_20191216.xlsx") %>% 
  rename_all(tolower) %>% 
  select(homewinterid, homeid, winterid, interventiondate, interventiontime) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         home_id = as.character(homeid),
         winter_id = as.character(winterid),
         intervention_date = interventiondate,
         intervention_time = interventiontime) %>% 
  select(home_winter_id, home_id, winter_id, intervention_date, intervention_time)
## Box location: All Files > NoonGroupData > KidsAIR > 
## 2019-November-Data > AK > Home Data > parentdemographics.xlsx
ak_parent_demographics_initial <-
  read_xlsx("Input/AK/ak_parent_demographics_20191216.xlsx") %>% 
  rename_all(tolower) %>% 
  select(homewinterid, gender, hispanic, race, income, education,
         totalres, underfive) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         gender_parent = as.factor(gender),
         hispanic_parent = as.factor(hispanic),
         race_parent = as.factor(race),
         income = as.factor(income),
         education = as.factor(education),
         total_residents = as.character(totalres),
         residents_under_five = as.character(underfive)) %>% 
  select(home_winter_id, gender_parent, hispanic_parent, race_parent,
         income, education, total_residents, residents_under_five) %>% 
  filter(!is.na(gender_parent))
# join all files from above
joined1 <- ak_homewinter_initial %>% 
  left_join(ak_parent_demographics_initial, by = "home_winter_id") %>% 
  left_join(ak_home_initial, by = "home_id") %>% 
  left_join(ak_child_initial, by = "home_id") %>% 
  mutate(area = "AK")

# create dataset of id's and treatment assignment
ak_home_ids_linked <- joined1 %>% 
  select(area, home_id, winter_id, home, home_winter_id, treatment) %>% 
  distinct(home_winter_id, .keep_all = TRUE) %>% 
  arrange(home_id, winter_id)

# create dataset of child demographic data
ak_child_demographics <- joined1 %>% 
  #distinct(child_id_num, .keep_all = TRUE) %>% 
  arrange(home_id, child_id_num, winter_id) %>% 
  filter(winter_id == 1 | winter_id == 2) 
# Save as RDS and CSV
write_rds(ak_home_ids_linked, "Output/ak_ids_linked.rds")
write_rds(ak_child_demographics, "Output/ak_demographic_data.rds")
```

# Combine linked id data for WMT, NN, AK
```{r}
ak_ids <- read_rds("Output/ak_ids_linked.rds")
nn_ids <- read_rds("Output/nn_ids_linked.rds")
wmt_ids <- read_rds("Output/wmt_ids_linked.rds")
kids_ids <- rbind(ak_ids, nn_ids, wmt_ids)
#write_rds(kids_ids, "Output/kids_linked_ids.rds")
kids_linked_ids <- read_rds("Output/kids_linked_ids.rds") %>% 
  mutate(winter_id = as.numeric(winter_id),
         winter_id = if_else(home == "CH218", winter_id + 1, winter_id)) %>% 
  filter(winter_id > 0)
#write_rds(kids_linked_ids, "Output/kids_linked_ids.rds")
```

# Combine demographic data for WMT, NN, AK
```{r}
ak_demographics <- read_rds("Output/ak_demographic_data.rds")
nn_demographics <- read_rds("Output/nn_demographic_data.rds")
wmt_demographics <- read_rds("Output/wmt_demographic_data.rds")
kids_demographics <- rbind(ak_demographics, nn_demographics, wmt_demographics)
# write_rds(kids_demographics, "Output/kids_combined_demographics.rds")
kids_demographics <- read_rds("Output/kids_combined_demographics.rds")
```

# Clean demographics data
```{r}
kids_demographics <- read_rds("Output/kids_combined_demographics.rds")
demographics_clean <- kids_demographics %>% 
  separate(intervention_time, c("trash", "intervention_time"), sep = " ") %>% 
  unite(intervention_datetime, c("intervention_date", "intervention_time"),
        sep = " ", remove = FALSE) %>% 
  mutate(intervention_datetime = ymd_hms(intervention_datetime)) %>% 
  select(-trash) %>% 
  mutate(home_winter_id = as.numeric(home_winter_id),
         home_winter_id = if_else(home == "CH218" & winter_id == 1, 77, home_winter_id),
         home_winter_id = if_else(home == "CH218" & winter_id == 2, 111, home_winter_id),
         home_winter_id = as.factor(home_winter_id)) 
# write_rds(demographics_clean, "Output/demographics_clean.rds")
```

>>>>

---
title: "EldersAIR initial home/adult data work"
author: "Ethan Walker"
date: "Started 10 Feb 2020, Updated 20 Feb 2020"
output: pdf_document
---

@@

# Load, format, and save home and adult overview/demographic data 
```{r}
# Load files 
## Box location: Update Box location once final data loaded
np_adult_initial <- read_xlsx("Input/NP/np_adult_20200220.xlsx") %>% 
  rename_all(tolower) %>% 
  mutate(adult_id_num = as.factor(adultid),
         home_id = as.factor(homeid),
         adult_id_char = as.factor(id),
         hispanic = as.factor(hispanic),
         race = as.factor(race),
         gender = as.factor(gender),
         consent_date = ymd(consentdate),
         area = "NP") %>% 
  select(adult_id_num, home_id, area, adult_id_char, hispanic, race, gender, consent_date) %>% 
  arrange(adult_id_num)

## Box location: Update Box location once final data loaded
nn_adult_initial <- read_xlsx("Input/NN/nn_adult_20200220.xlsx") %>% 
  rename_all(tolower) %>% 
  mutate(adult_id_num = as.factor(adultid),
         home_id = as.factor(homeid),
         adult_id_char = as.factor(id),
         hispanic = as.factor(hispanic),
         race = as.factor(race),
         gender = as.factor(gender),
         consent_date = ymd(consentdate),
         area = "NN") %>% 
  select(adult_id_num, home_id, area, adult_id_char, hispanic, race, gender, consent_date) %>% 
  arrange(adult_id_num)

elders_adult <- rbind(np_adult_initial, nn_adult_initial)

## Box location: Update Box location once final data loaded
np_homewinter_initial <- read_xlsx("Input/NP/np_homewinter_20200220.xlsx") %>% 
  rename_all(tolower) %>% 
  separate(interventiontime, c("trash1", "intervention_time"), sep = " ", remove = FALSE) %>%
  separate(samplingtime, c("trash1", "sampling_time_1"), sep = " ", remove = FALSE) %>%
  separate(pickuptime, c("trash1", "pickup_time_1"), sep = " ", remove = FALSE) %>%
  separate(sampling2time, c("trash1", "sampling_time_2"), sep = " ", remove = FALSE) %>%
  separate(pickup2time, c("trash1", "pickup_time_2"), sep = " ", remove = FALSE) %>%
  mutate(home_id = as.factor(homeid),
         winter_id = as.factor(winterid),
         home_winter_id = as.factor(homewinterid),
         intervention_date = ymd(interventiondate),
         intervention_time = as.character(intervention_time),
         sampling_date_1 = ymd(samplingdate),
         sampling_time_1 = as.character(sampling_time_1),
         pickup_date_1 = ymd(pickupdate),
         pickup_time_1 = as.character(pickup_time_1),
         sampling_date_2 = ymd(sampling2date),
         sampling_time_2 = as.character(sampling_time_2),
         pickup_date_2 = ymd(pickup2date),
         pickup_time_2 = as.character(pickup_time_2),
         area = "NP") %>% 
  select(home_id, winter_id, home_winter_id, area, intervention_date, intervention_time,
         sampling_date_1, sampling_time_1, pickup_date_1, pickup_time_1,
         sampling_date_2, sampling_time_2, pickup_date_2, pickup_time_2) %>% 
  filter(!is.na(home_id)) %>% 
  arrange(home_id, winter_id)

## Box location: Update Box location once final data loaded
nn_homewinter_initial <- read_xlsx("Input/NN/nn_homewinter_20200220.xlsx") %>% 
  rename_all(tolower) %>% 
  separate(interventiontime, c("trash1", "intervention_time"), sep = " ", remove = FALSE) %>%
  separate(samplingtime, c("trash1", "sampling_time_1"), sep = " ", remove = FALSE) %>%
  separate(pickuptime, c("trash1", "pickup_time_1"), sep = " ", remove = FALSE) %>%
  separate(sampling2time, c("trash1", "sampling_time_2"), sep = " ", remove = FALSE) %>%
  separate(pickup2time, c("trash1", "pickup_time_2"), sep = " ", remove = FALSE) %>%
  mutate(home_id = as.factor(homeid),
         winter_id = as.factor(winterid),
         home_winter_id = as.factor(homewinterid),
         intervention_date = ymd(interventiondate),
         intervention_time = as.character(intervention_time),
         sampling_date_1 = ymd(samplingdate),
         sampling_time_1 = as.character(sampling_time_1),
         pickup_date_1 = ymd(pickupdate),
         pickup_time_1 = as.character(pickup_time_1),
         sampling_date_2 = ymd(sampling2date),
         sampling_time_2 = as.character(sampling_time_2),
         pickup_date_2 = ymd(pickup2date),
         pickup_time_2 = as.character(pickup_time_2),
         area = "NN") %>% 
  select(home_id, winter_id, home_winter_id, area, intervention_date, intervention_time,
         sampling_date_1, sampling_time_1, pickup_date_1, pickup_time_1,
         sampling_date_2, sampling_time_2, pickup_date_2, pickup_time_2) %>% 
  filter(!is.na(home_id)) %>% 
  arrange(home_id, winter_id)

elders_homewinter <- rbind(np_homewinter_initial, nn_homewinter_initial)

## Box location: Update Box location once final data loaded
np_home_initial <- read_xlsx("Input/NP/np_home_20200220.xlsx") %>% 
  rename_all(tolower) %>% 
  mutate(home_id = as.factor(homeid),
         home = as.factor(home),
         treatment = as.factor(txcondition),
         area = "NP") %>% 
  select(home_id, home, treatment, area)

## Box location: Update Box location once final data loaded
nn_home_initial <- read_xlsx("Input/NN/nn_home_20200220.xlsx") %>% 
  rename_all(tolower) %>% 
  mutate(home_id = as.factor(homeid),
         home = as.factor(home),
         treatment = as.factor(txcondition),
         area = "NN") %>% 
  select(home_id, home, treatment, area)

elders_home <- rbind(np_home_initial, nn_home_initial)
```

# Combine adult, home, homewinter files
```{r}
elders_ids_linked <- elders_homewinter %>% 
  left_join(elders_home, by = c("area", "home_id")) %>% 
  left_join(elders_adult, by = c("area", "home_id")) %>% 
  mutate(home = str_remove(home, "[_]"))
#write_rds(elders_ids_linked, "Output/elders_ids_linked.rds")
```
